CAD and Routing Architecture for Interposer-Based Multi-FPGA Systems

### 2014-11-11 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
minor fixes
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4502 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

Previous work by Andre et al ~\cite{hahn2014cad} modified the rrgraph by directly removing \textit{\% wires cut} percent of edges from the graph at nodes located at the cutline and increased the switch delay of the remaining edges of the nodes at the cutline. While this is a reasonable method to model such architectures, it makes it difficult to experiment with different routing-interposer interfaces such as placing input muxes for interposer wires. Therefore, we modify the rrgraph differently to more accurately reflect the interposer layer:

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{vpr_gui.eps}
\caption{VPR Graphical User Interface. Left:Full chip view. Right:Connectivity at the cutline. Interposer wires are drawn in red. Due to limited number of interposer wires, some vertical routing wires are not able to connect to any interposer wire and are left dangling. Routing wires do not crosses the cutline.}
\label{fig:vpr_interposer_gui}
\end{figure*}

@@

In~\cite{hahn2014cad}, Andre et al. tested several different \textit{cut\_cost} formulations, as well as different weighting for each. They found that the following \textit{cut\_cost} results in the best quality of results in terms of minimum routable channel width and critical path delay.

>>>>

Previous work by Pereira et al ~\cite{hahn2014cad} modified the rrgraph by directly removing \textit{\% wires cut} percent of edges from the graph at nodes located at the cutline and increased the switch delay of the remaining edges of the nodes at the cutline. While this is a reasonable method to model such architectures, it makes it difficult to experiment with different routing-interposer interfaces such as placing input muxes for interposer wires. Therefore, we modify the rrgraph differently to more accurately reflect the interposer layer:

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{vpr_gui.eps}
\caption{VPR Graphical User Interface. Left:Full chip view. Right:Connectivity at the cutline. Interposer wires are drawn in red. Due to limited capacity of the interposer, some vertical routing wires are left dangling. Routing wires do not cross the cutline unless via a connection to an interposer wire.}
\label{fig:vpr_interposer_gui}
\end{figure*}

@@

In~\cite{hahn2014cad}, Pereira et al tested several different \textit{cut\_cost} formulations, as well as different weighting for each. They found that the following \textit{cut\_cost} results in the best quality of results in terms of minimum routable channel width and critical path delay.
